Scoring epidemiological forecasts on transformed scales

### 2023-08-17 final submission after reformatting/final-manuscript.tex
Change order of Figures in tex file
add reference to S2 Fig
Remove references to figures for the practical example so that figures are mentioned in order as required by PLOS

\subsection*{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Fig \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Fig \ref{fig:HUB-cors}A, rankings between models in practice stay quite stable for a single forecast.

@@

Overall model rankings would be expected to differ more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores usually is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above (see Fig \ref{fig:HUB-cors} for a practical example). Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on how different models perform across targets of different orders of magnitude, rankings in terms of average scores may change when applying a transformation.

@@

In practice, one issue with the log transform is that it is not readily applicable to negative or zero values, which need to be removed or otherwise handled. 
One common approach to this end is to add a small positive quantity, such as $a = 1$, to all observations and predictions before taking the logarithm \cite{bellegoDealingLogsZeros2022}. This still represents a strictly monotonic transformation, but the choice of $a$ does influence scores and rankings (measures of relative errors shrink the larger the chosen value $a$). As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ thus balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined in the previous sections. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts of small quantities. For increasing $a$, less relative weight is given to smaller forecast targets. For very large values of $a$, $\log(x + a)$ is roughly linear in $x$, so that using a very large $a$ implies similar relative weighting as applying no transformation at all. In practice, a user could explore the effect of different values of $a$ graphically and choose $a$ such that the relative weightings of times and regions with high and low incidence correspond to their preferences (see Fig \ref{fig:HUB-log-different-offsets} in our example application).

@@

All predictive quantiles were truncated at 0. We applied the log-transformation after adding a constant $a = 1$ to all predictions and observed values. The choice of $a = 1$ in part reflects convention, but also represents a suitable choice as it avoids giving excessive weight to forecasts close to zero, while at the same time ensuring that scores for observations $> 5$ can be interpreted reasonably. The analysis was conducted in \texttt{R} \cite{R}, using the \texttt{scoringutils} package \cite{bosseEvaluatingForecastsScoringutils2022} for forecast evaluation. All code is available on GitHub 
(\url{https://github.com/epiforecasts/transformation-forecast-evaluation}). Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

>>>>

\subsection*{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Fig \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as illustrated in our practical example, rankings between models in practice stay quite stable for a single forecast.

@@

Overall model rankings would be expected to differ more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores usually is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above. Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on how different models perform across targets of different orders of magnitude, rankings in terms of average scores may change when applying a transformation.

@@

In practice, one issue with the log transform is that it is not readily applicable to negative or zero values, which need to be removed or otherwise handled. 
One common approach to this end is to add a small positive quantity, such as $a = 1$, to all observations and predictions before taking the logarithm \cite{bellegoDealingLogsZeros2022}. This still represents a strictly monotonic transformation, but the choice of $a$ does influence scores and rankings (measures of relative errors shrink the larger the chosen value $a$). As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ thus balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined in the previous sections. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts of small quantities. For increasing $a$, less relative weight is given to smaller forecast targets. For very large values of $a$, $\log(x + a)$ is roughly linear in $x$, so that using a very large $a$ implies similar relative weighting as applying no transformation at all. In practice, a user could explore the effect of different values of $a$ graphically and choose $a$ such that the relative weightings of times and regions with high and low incidence correspond to their preferences.

@@

All predictive quantiles were truncated at 0. We applied the log-transformation after adding a constant $a = 1$ to all predictions and observed values. The choice of $a = 1$ in part reflects convention, but also represents a suitable choice as it avoids giving excessive weight to forecasts close to zero, while at the same time ensuring that scores for observations $> 5$ can be interpreted reasonably. \nameref{fig:illustration-effect-log-offset} illustrates the effect of adding a small quantity before taking the logarithm. The analysis was conducted in \texttt{R} \cite{R}, using the \texttt{scoringutils} package \cite{bosseEvaluatingForecastsScoringutils2022} for forecast evaluation. All code is available on GitHub 
(\url{https://github.com/epiforecasts/transformation-forecast-evaluation}). Where not otherwise stated, we report results for a two-week-ahead forecast horizon.
